---
title: "Generate random draws of VE"
author: "Dan Weinberger"
date: "8/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmlTable)
```

## Read in the function

**obs.VEs** should be a vector with 3 values: *mean, LCL, UCL* of reported Vaccine Effectiveness

**Nsim** is number of draws you want from the distribution

**Returns nsim values of the VE** based on the observed distribution

```{r}
source('./R/sim_ve.R')
```

Here is a single call to the function, with mean VE=98 and 95%CI (79, 100):

```{r}
  test1 <- VE_dist_func(obs.VEs = c(98, 79, 100), nsim = 10000)


```

### Distribution of the VE

```{r}
hist(test1)
```

### Empirical 95% CI of VE from the simulated data

This shows that we are correctly recovering the coverage of the 95% CIs with the simulated data

```{r}
round(quantile(test1, probs=c(0.5, 0.025, 0.975)),1)
```

## Read in some summary data and metadata for multiple serotypes

```{r}
data1 <- list(
  list(
    'study' = 'Andrews',
    'serotype' = '4',
    'dose' = '1+',
    'age' = '2.5m_12m',
    've' = c(96.9, 81.6, 99.5)
  ),
  list(
    'study' = 'Andrews',
    'serotype' = '6B',
    'dose' = '1+',
    'age' = '2.5m_12m',
    've' = c(54.9, 4.3, 78.7)
  ),
  list(
    'study' = 'Andrews',
    'serotype' = '6B',
    'dose' = '2_prim_or_1_boost',
    'age' = '4_12m',
    've' = c(60, -2.7, 84.5)
  )
)
```

## Call the function for multiple serotypes

\#obs.VEs should be vector with 3 values: mean, LCL, UCL of reported Vaccine Effectiveness

```{r}
  test2 <- lapply(data1, function(x){
    ve.est <- VE_dist_func(x$ve) 
    out.list <- list('ve.est'=ve.est,'metadata'=x)
    return(out.list)
  }
    )
  
  
```

Extract just the VE estimates

```{r}
ve.test2 <- lapply(test2, '[[','ve.est')
```

Calculate empirical 95% CIs from the simulated data

```{r}

ve.test2.q <- round(t(sapply(ve.test2, quantile, probs=c(0.5, 0.025, 0.975))),1)


```

Format the simulated values

```{r}

ve.test2.q.fmt <- paste0(ve.test2.q[,'50%'], ', (' ,ve.test2.q[,'2.5%'] ,', ' , ve.test2.q[,'97.5%'],')'  )

print(ve.test2.q.fmt)
```

Extract the observed VEs

```{r}
obs.VEs <- t(sapply(test2, function(x) x$metadata$ve))

obs.VEs.fmt <- paste0(obs.VEs[,1], ', (' ,obs.VEs[,2] ,', ' , obs.VEs[,3],')'  )


```

## Compare the input and output data

```{r}

htmlTable(cbind.data.frame('Input'=obs.VEs.fmt,'Output'=ve.test2.q.fmt))
```
